Plots and tables summarizing results of Poisson simulations

### 2019-12-16 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

```{r plot-bursts-function, fig.height=4, fig.width=8}
mu.bur <- bursts.f(t)
plot(t,mu.bur,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

@@

```{r plot-cb-function, fig.height=4, fig.width=8}
mu.cb <- cblocks.f(t)
plot(t,mu.cb,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

@@

```{r plot-bumps-function, fig.height=4, fig.width=8}
mu.b <- bumps.f(t)
plot(t,mu.b,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

>>>>

```{r plot-bursts-function, fig.height=2.5, fig.width=8}
mu.bur <- 0.01 + bursts.f(t)
x      <- rpois(n,mu.bur)
create.signal.plot(mu.bur,x)
```

@@

```{r plot-cb-function, fig.height=4, fig.width=8}
mu.cb <- 0.01 + cblocks.f(t)
x     <- rpois(n,mu.cb)
create.signal.plot(mu.cb,x)
```

@@

```{r plot-bumps-function, fig.height=4, fig.width=8}
mu.b <- 0.01 + bumps.f(t)
x    <- rpois(n,mu.b)
create.signal.plot(mu.b,x)
```
